---
title: "Assignment 1"
author: "Nathaniel Gunter"
date: "1/13/2020"
output: 
  html_document:
    toc: yes
    toc_float: yes
    highlights: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(extrafont)
#loadfonts(device="win")
```

15/15 questions completed

## 1
The final course grade is worked as a combination of four assignments, sixteen labs with additional classroom exercises, two projects, daily clicker quizzes, online chapter quizzes, two midterm exams, and the final exam. The class is graded on a ten point scale, i.e. 90-100% is an A, 80-90% is a B, etc. The specific grade calculation follows the function $$grade = (0.15\times \frac{\sum Assignment Grades}{4}+0.1\times \frac{\sum Labs and Classroom Exercises}{16}\\+0.1\times (\frac{1}{3}\times Project 1+ \frac{2}{3} \times Project 2)+0.1\times Average Clicker Score + 0.05 \times Average Canvas Quiz Grade \\+ 0.2 \times \frac{\sum Midterms}{2}+0.3\times Final Exam)\times 100\%$$

## 2

```{r loadDDT}
ddt<-read.csv("DDT.csv")
```

### a)

build using the following: 
```{r buildCoplot}
ddtPlot <- with(ddt, coplot(LENGTH ~ WEIGHT | RIVER * SPECIES, col = MILE))
```

### b)

Each plot is a scatterplot of the weight vs length of catfish caught at the mouth of Flint Creek, Limstone Creek, or Spring Creek, from left to right. All three plots show the qualitatively similar trend that length and weight are positively correlated

### c)

Line A returns a vector of values, each of which is the number of miles upstream that a fish in the table was caught. The vector is then stored in the object 'm'.

### d)

Line B gives the number of unique values in 'm'. This correlates with the number of sites in the experiment where they caught fish.

### e)

The top six plots are empty because no largemouth bass or smallmouth bass were caught in the tributary creeks, so there are no data for graphs given those parameters.

### f)

```{r meanDDT}
catFCM<-subset(ddt,RIVER=="FCM"&SPECIES=="CCATFISH")
mean(catFCM$DDT)
```

The mean DDT value for catfish caught in the FCM river is 45.

## 3

### a)

Maximum span length is a quantitative variable.

### b)

Number of vehicle lanes is quantitatitve.

### c)

Presence/absence of a toll bridge is qualitative.

### d)

Average daily traffic is either quantitative or qualitative depending on whether it is reported as number of vehicles or simply "low", "medium", and "high".

### e)

Deck condition is a qualitative variable.

### f)

Bypass/detour length is a quantitative variable.

### g)

Route type is a qualitative variable.

## 4

MS pg 12-13

### a)
What are the names of the four random sampling designs (one simple and three complex)?

The four random sampling designs are simple random sampling, stratified random sampling, cluster sampling, and systematic sampling.

### b)

Give a brief description of each.

Simple random sampling is as sample of size $n$ selected from the population such that every sample of the same size has the same chance of selection.

Stratified random sampling first divides the population into two or more groups (called strata) based on some factor, then randomly samples from each stratum. The random samples are then combined into the final sample.

Cluster sampling first randomly selects natural groupings of the data, then selects randomly data from within each cluster for the sample.

Systematic sampling selects every $k$th unit from a list of experimental units.

## 5

```{r}
mtbe.dat<-read.csv('MTBE.csv')
ind<-sample(1:dim(mtbe.dat)[1],5,replace = FALSE)
mtbe.samp<-mtbe.dat[ind,]
mtbe.samp 
```
### a)

#### i)

```{r}
mtbe.o<-na.omit(mtbe.dat)
```

#### ii)

```{r}
mtbe.depth<-mtbe.o[mtbe.o$Aquifier=="Bedrock",]$Depth
sd(mtbe.depth)
```

## 6 
MS 1.16 p 15

```{r}
earth.dat<-read.csv("EARTHQUAKE.csv")
ind<-sample(1:dim(earth.dat)[1],30,replace=FALSE)
earth.samp<-earth.dat[ind,]
earth.samp
```

### a)

#### i)

```{r}
plot(ts(earth.samp))
```

#### ii)

```{r}
median(earth.samp$MAGNITUDE)
```

## 7 

MS STATISICS IN ACTION

### a)

What is the data collection method?

The data collection method is stratified sampling, where the ppulation was stratified by location of the catch. 

### b)

What is the population?

The population is all fish in the Tennessee River and its tributaries.

### c)

Give the names of all qualitative variables.

The qualitative variables were RIVER and SPECIES.

## 8
MS 2.1 pg 26

### a)

A barplot is used to describe the data in this case.

### b)

The measured variable was type of robotic limb used in the robot design.

### c)

Currently, the most used robot design is legs only. 

### d)

#### none

```{r}
round(15/106,2)
```

#### both

```{r}
round(8/106,2)
```

#### legs only

```{r}
round(63/106,2)
```

#### wheels only

```{r}
round(20/106,2)
```

### e)

```{r, echo=FALSE}
pareto<-function(x,mn="Pareto barplot",...){  # x is a vector
x.tab=table(x)
xx.tab=sort(x.tab, decreasing=TRUE,index.return=FALSE)
cumsum(as.vector(xx.tab))->cs
length(x.tab)->lenx
bp<-barplot(xx.tab,ylim=c(0,max(cs)),las=2)
lb<-seq(0,cs[lenx],l=11)
axis(side=4,at=lb,labels=paste(seq(0,100,length=11),"%",sep=""),las=1,line=-1,col="Blue",col.axis="Red")
for(i in 1:(lenx-1)){
segments(bp[i],cs[i],bp[i+1],cs[i+1],col=i,lwd=2)
}
title(main=mn,...)

}
```

```{r}
freq = c(15,8,63,20)
RL = c("None", "Both","LegsO","WheelsO")
l= rep(RL,freq)
pareto(l)
```

## 9
MS 2.4 pg 27 

### a)

```{r}
freq=c(32,6,12)
name=c("Windows","Explorer","Office")
pie(freq,name)
```

According to this pie chart, Explorer had the lowest proportion of security issues. 

### b)

```{r}
breach.freq=c(6,8,22,3,11)
breach.type=c("Den. of Serv.","Info Discl.", "Rem Code Exec", "Spoofing","Priv Elev")
breach.pare=rep(breach.type,breach.freq)
pareto(breach.pare)
```

Based on the Pareto graph, I would advise Microsoft to focus on the remote code execution repercussion.

## 10 
MS 2.10 pg 28

## 11
MS 2.72 pg 70

## 12 
MS 2.73 pg 70

## 13
MS 2.80 pg 72

## 14
MS 2.84 pg 74

## 15
```{r boxplot}
boxplots <-ddt%>%ggplot(aes(x=RIVER,y=LENGTH,fill=SPECIES))+geom_boxplot()+ggtitle("Nathaniel Gunter")
#+theme(text=element_text(size=16,family="TT Courier New"))
boxplots
```  