---
title: "Assignment 1"
author: "Nathaniel Gunter"
date: "1/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(extrafont)
loadfonts(device="win")
```
# Assignement 1

## 1
The final course grade is worked as a combination of four assignments, sixteen labs with additional classroom exercises, two projects, daily clicker quizzes, online chapter quizzes, two midterm exams, and the final exam. The class is graded on a ten point scale.

TODO: Add percentages, figure out how to link with LaTeX so that the calculation can be displayed properly.

## 2
```{r loadDDT}
ddt<-read.csv("DDT.csv")
```
SKETCH: Load DDT.csv
### a)
build using the following: 
```{r buildCoplot}
ddtPlot <- ddt %>% coplot(LENGTH ~ WEIGHT | RIVER*SPECIES)
```
coplot(LENGHT ~ WEIGHT | RIVER*SPECIES) plus a few options
### b)
Learn how to interpret coplots
### c)
see b)
### d)
see b)
### e)
see b)
### f)
```{r meanDDT}
catFCM<-subset(ddt,RIVER=="FCM"&SPECIES=="CCATFISH")
mean(catFCM$DDT)
```

## 3
MS 1.14-pg 8

## 4
MS pg 12-13
### a)
What are the names of the four random sampling designs (one simple and three complex)?
### b)
Give a brief description of each

## 5
MS 1.15 pg 15 

## 6 
MS 1.16 p 15

## 7 
MS STATISICS IN ACTION
### a)
What is the data collection method?
### b)
What is the population?
### c)
Give the names of all qualitative variables.

## 8
MS 2.1 pg 26

## 9
MS 2.4 pg 27 

## 10 
MS 2.10 pg 28

## 11
MS 2.72 pg 70

## 12 
MS 2.73 pg 70

## 13
MS 2.80 pg 72

## 14
MS 2.84 pg 74

## 15
```{r boxplot}
boxplots <-ddt%>%ggplot(aes(x=RIVER,y=LENGTH,fill=SPECIES))+geom_boxplot()+ggtitle("Nathaniel Gunter")
#+theme(text=element_text(size=16,family="TT Courier New"))
boxplots
```  